Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-02-06 TEBenchmarkPaper/article.tex
Flesh out a comment

%we limit our discussion to systems which work in maths: there are
%others which work in scientific discovery which are also relevant.

>>>>

We limit our discussion to applications in mathematics, although there are
similar approaches being applied to the task of \emph{scientific} discovery.
Scientific knowledge relies on inductive reasoning and experimental testing,
which are not so important to a mathematical theory. However, these techniques
do play an important role in many of the tools we investigate: in particular,
inductive reasoning allows a system to conjecture statements which may be too
difficult for it to deductively prove; whilst experimental testing, e.g. by
checking universally-quantified statements against some specific values, allows
many falsehoods to be quickly discarded without requiring more elaborate
symbolic reasoning.
